Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex
Figure Adjustments

\begin{figure*}[t]
  \centering
  \includegraphics[keepaspectratio, width=\textwidth]{user_figure.png}
  \vspace{-26 pt}
  \caption{\normalfont Left: The flow diagram showing how therapists and children exchange data through the game and the portal. Right: The game, {\em Kimbee}, where children play the role of a bee trying to collect honey as a resource along the way.}
  \label{fig:user}
\end{figure*}

@@

\subsubsection{Game (Kimbee)}

@@

After every challenge, the audio spoken by the child is encoded and sent to the central data server, see Figure \ref{fig:user} for a diagram of this.

\subsubsection{Therapist Portal}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[keepaspectratio, width=\textwidth]{tech_figure.png}
  \caption{\normalfont Left: The Therapist Portal, the user system of the therapist. Middle: The Central Server, hosts the recordings and facilitates interactions. Right: The Kimbee Game, interactive game that allows practice of speech for children. }
  \label{fig:tech}
\end{figure*}

>>>>

\begin{figure*}[t]
  \centering
  \includegraphics[keepaspectratio, width=\textwidth]{user_figure.png}
  \vspace{-22 pt}
  \caption{\normalfont Left: The game, {\em Kimbee}, where children play the role of a bee trying to collect honey as a resource. Right: The flow diagram showing how therapists and children exchange data through the game and the portal.}
  \label{fig:user}
\end{figure*}

@@

\subsubsection{Gameplay}

@@

After every challenge, the audio spoken by the child is encoded and sent to the central data server, see Figure \ref{fig:user} for a diagram of this. These data can be examined and reviewed in the therapist portal.

\subsubsection{Therapist Review}

@@

\begin{figure*}[t]
  \centering
  \includegraphics[keepaspectratio, width=\textwidth]{tech_figure.png}
  \vspace{-22 pt}
  \caption{\normalfont Left: The Therapist Portal, the user system of the therapist. Middle: The Central Server, hosts the recordings and facilitates interactions. Right: The Kimbee Game, interactive game that allows practice of speech for children. }
  \label{fig:tech}
\end{figure*}
